\documentclass{beamer}
\usepackage{graphicx}
\usetheme{Madrid}
\title{F prog semester project}
\author{Maximilian Jakob Maag, Skyler Mayfield, Catrina David}
\useoutertheme{miniframes}
\useinnertheme{circles}
\date{\today}

\begin{document}
	\begin{frame}
		\titlepage
	\end{frame}
	\begin{frame}
		\frametitle{Table of Content}
		\begin{itemize}
			\item Reflection on baseline
			\item Reflection on purely functional approach
			\item Compare between approaches
		\end{itemize}
	\end{frame}
	\begin{frame}
		\frametitle{Reflection baseline}
		\begin{itemize}
            \item Less functional.
            \item We put effort into developer experience and tooling, which slowed us down at the beginning.
            \item Once the tooling worked properly, it made the development process much easier.
            \item It was hard to get into functional thinking; we used mostly object-oriented principles.
            \item Implementing more small examples would have made things easier.
			\item A less graphical exam to start. Learning by implementing mathmetical functions would be easier.
		\end{itemize}
	\end{frame}
	\begin{frame}
		\frametitle{Reflection purely functional}
		\begin{itemize}
			\item Immutable datastructures, closures, higher order functions.
			\item It was very hard to implement a functional architecture for the first time.
			\item A working sample project that is purely functional could help understanding the paradigma better.
		\end{itemize}
	\end{frame}
	\begin{frame}
		\frametitle{Reflection in comparison}
		\begin{itemize}
			\item Software is less complex.
			\item It can be extended with futher functions very easy.
			\item Testcode can test the code functionwise.
		\end{itemize}
	\end{frame}
\end{document}
